### 2017-08-29 Sections/mathematical_representation_of_quantum_networks.tex
minor

\subsection{Network costs \& attributes} \label{sec:costs} \index{Costs}\index{Attributes}

The edge weights in $G$ represent the \textit{costs} ($\vec c$) and \textit{attributes} ($\vec a$) associated with using that link. In general these needn't be single numbers, but would rather be sets, representing different types of costs and attributes of links, of which there may be many. These could include, for example, latency, bandwidth, dollar cost, and quality.

>>>>

\subsection{Cost vector analysis} \label{sec:costs} \index{Cost vectors}\index{Attributes}

The edge weights in $G$ represent the \textit{costs} ($\vec c$) and \textit{attributes} ($\vec a$) associated with using that link. In general these needn't be single numbers, but would rather be sets or data-structures, representing different types of costs and attributes of links, of which there may be many. These could include, for example, latency, bandwidth, dollar cost, and quality measures.
